Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/inverted_u.tex

\section{Competition vs Better Algorithms}\label{section:5}

\swedit{Now we demonstrate the inverted-U relationship between the
  incentivized algorithms and the competition levels in the game. In
  the order of increasing competition levels, we study three different
  settings: permanent monopoly, temporary monopoly, and permanent
  duopoly. In more details:}

@@

\swedit{\xhdr{Permanent Monopoly.} There is only a single firm in the market
for the entire period. In this case, the firm will can the entire
market, regardless what algorithm it deploys. Assuming the deployment
of any exploration algorithms will incur certain cost, then the firm
would choose to deploy $\DG$.}

@@

\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$, in a simulation where the agent alive at $t-1$ and the agent alive at $t$ choose different firms.
\end{definition}

>>>>

\section{Competition vs Better Algorithms}\label{section:5}
\swedit{how about just name the section ``inverted U''?}  \swedit{Now
  we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. First, the
  story for permanent monopoly is relatively straightforward.}

@@

\swedit{\xhdr{Permanent Monopoly.} Since there is only a single firm
  in the market for the entire period, the firm can take the entire
  market regardless what algorithm it deploys. Assuming the deployment
  of any exploration algorithms will incur certain cost, the firm
  would choose to deploy $\DG$.}

Next, to describe our results for temporary monopoly, we will
introduce the following notion of \textit{effective end of game
  (EEOG)} --- the last round $t$ such that the agent at round $(t-1)$
and the next agent around at $t$ choose different firms.

@@

\OMIT{
\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$, in a simulation where the agent alive at $t-1$ and the agent alive at $t$ choose different firms.
\end{definition}
}
